# Pesos de alumnos

A quote:
> Este es un test

    a lovely quiet paragraph
      no code exists
        still a valid knitr document

-- My haiku on an empty document


La media de los pesos de 500 estudiantes de un colegio es 70 kg y la desviacion tipica 3 kg. Suponiendo que los pesos se distribuyen normalmente, hallar cuantos estudiantes pesan: es nuestra valor
<!--
```{r model, collapse=TRUE}
options(digits = 7)
fit <- lm(regFormula(), data = mtcars)
b   <- coef(fit)
summary(fit)
#input$area_CalDis
#library(shiny)
#textOutput("area_CalDis")
```
-->
The fitting result is $mpg = `r b[1]` + `r b[2]``r input$x`$.
Below is a scatter plot with the regression line.

```{r plot, fig.height=5}
par(mar = c(4, 4, 1, 1))
plot(regFormula(), data = mtcars, pch = 19, col = 'gray')
abline(fit, col = 'red', lwd = 2)
```

# A Minimal Example

We examine the relationship between speed and stopping
distance using a linear regression model:
$Y = \beta_0 + \beta_1 x + \epsilon$.

```{r modelo, fig.width=5, fig.height=4}
par(mar = c(4, 4, 1, 1), mgp = c(2, 1, 0), cex = 0.8)
plot(cars, pch = 20, col = 'darkgray')
fit <- lm(dist ~ speed, data = cars)
abline(fit, lwd = 2)
```

The slope of a simple linear regression is `r coef(fit)[2]`.
